---
title: "COVID-19 at UFindlay"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: ["facebook", "twitter", "linkedin"]
    vertical_layout: fill
---

```{r setup, include=FALSE}
#-----------Packages---------------
library(flexdashboard)
`%>%` <- magrittr::`%>%`

#----------Data--------------------
library(googlesheets4)
ufc19 <- read_sheet("1xjwASri8-Ozw5QkEOEuE-UH8BFOLe-t4rbiMqFzB9BA")

totalConf <- ufc19$total %>% max()
total_tests <- ufc19$total_tests %>% max()
positivity <- dplyr::filter(ufc19, ufc19$date == max(ufc19$date))[8]
activeNow <- dplyr::filter(ufc19, ufc19$date == max(ufc19$date))[3]
totalDead <- ufc19$deaths %>% max()
quarantine <- dplyr::filter(ufc19, ufc19$date == max(ufc19$date))[9]
long_avg <- round(totalConf/total_tests*100, 0)

```

Dashboard
=======================================================================

Row {data-width = 400}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}
valueBox(
  value = paste(totalConf, " (", max(activeNow), ")", sep = ""),
  caption = "Total confirmed cases (active now)",
  color = "#ff8300",
  icon = "fas fa-user-md"
)
```

### quarantine {.value-box}

```{r}
valueBox(
  value = quarantine,
  caption = "Students in quarantine",
  color = "#ebe355",
  icon = "ion-android-home"
)
```

### positivity {.value-box}

```{r}
valueBox(
  value = paste(round(positivity,digits=2)*100, "% (", long_avg, "%)", sep = ""),
  caption = "Weekly positivity (average since Aug 17)",
  color = "#644a8c",
  icon = "ion-android-add-circle"
)

```


Row 
-----------------------------------------------------------------------

### **Cumulative Cases by Type**

```{r}
plotly::plot_ly(data = ufc19) %>%
  plotly::add_trace(
    x = ~date, 
    y = ~total, 
    type = 'scatter', 
    name= "Confirmed", 
    mode = "lines+markers"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~deaths, 
    type = 'scatter',
    name = 'Deaths', 
    mode = 'lines+markers'
  ) %>%
  plotly::layout(
    xaxis=list(title = ""),
    yaxis = list(title = "Cumulative Number of Cases"),
    hovermode  = "compare"
  )
```


### **Key Trends:** Active Cases

```{r}

plotly::plot_ly(data = ufc19) %>%
  plotly::add_trace(
    x = ~date, 
    y = ~active, 
    type = 'scatter', 
    name= "Active", 
    mode = "lines+markers"
  ) %>%
  plotly::layout(
    xaxis=list(title = ""),
    yaxis = list(title = "Active cases")
  )
```

About
=======================================================================

**The University of Findlay Coronavirus Dashboard** 

The [UF Coronavirus Dashboard](https://bioben20.github.io/findlay_coviddash) provides a record of COVID-19 cases at the [University of Findlay](https://www.findlay.edu/) during the Fall 2020 semester. Students returned to campus on August 17, 2020, and most classes are taught in hybrid, hyflex, or online format. Masks are required in buildings to reduce spread of coronavirus, and classrooms are limited to half of their seating capacity.

**Data**

The data for this dashboard are obtained from the University of Findlay [Start Safe & Stay Safe Covid Dashboard](https://www.findlay.edu/oiler-start-safe-and-stay-safe/covid-dashboard), which provides a weekly snapshot of COVID-19 cases reported by Cosiano Health Center. According to the dashboard, "case information is gathered from cases of students and employees tested at the University's Cosiano Health Center. In addition, any cases involving students or employees that are reported to the Health Center will be included, once the test is confirmed." Community cases processed by Cosiano are not included in this dashboard.

On October 9, 15, and 22, the University of Findlay made testing available to the campus community on a voluntary basis. The University does not distinguish symptomatic and asymptomatic cases in their weekly report. Prior to these events, Cosiano Health Center processed an average of 52 tests per week. For the weeks of Oct 9-22, Cosiano reported an average of 310 tests per week.

*Data is current as of **`r format(max(ufc19$date), "%A, %B %d, %Y")`***

**Development**

This dashboard was built by [Ben Dolan](https://www.biologyben.com/) in RStudio using [Flexdashboard](http://rmarkdown.rstudio.com/flexdashboard/) and is hosted on [Github Pages](https://pages.github.com/).